A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Add expressions for CRAN packages

\begin{table*}[tb]
  \centering
  \begin{tabular}{l|rr} \hline
    Expression & Eval Call & Eval Call \% \\\hline
    \c{c("auto", "shell", "radix")} & 1987105 & 29.3\%\\
    \c{c("auto", "shell", "quick", "radix")} & 1593169  & 23.5\%\\
    \c{local(\{info <- loadingNamespaceInfo(...} & 1008632 &       14.9\%\\
    \c{c("onLoad", "attach", "detach", "onUnload")}   & 470566 &      6.9\%\\
    \c{c("append", "prepend", "replace")} &              261587&       3.9\% \\
    \c{c("left", "right", "centre", "none")} & 162086     & 2.4\%\\
    \c{c("no", "ifany", "always")}   &                71580 &       1.1\%\\
    \c{c("pearson", "kendall", "spearman")}  & 72962 &      1.1\%\\
    \c{NULL}& 75330  &      1.1\% \\
    \c{Integer Vector}&                 66279&       1\%\\
  \end{tabular}
  \caption{Top ten eval calls in CRAN}
  \label{A}
\end{table*}

>>>>

The most frequent ten expressions to eval calls from core R contribute to
85.2\% of all \eval calls.
\begin{table*}[tb]
  \centering
  \begin{tabular}{l|rr} \hline
    Expression & Eval Call & Eval Call \% \\\hline
    \c{c("auto", "shell", "radix")} & 1987105 & 29.3\%\\
    \c{c("auto", "shell", "quick", "radix")} & 1593169  & 23.5\%\\
    \c{local(\{info <- loadingNamespaceInfo(...} & 1008632 &       14.9\%\\
    \c{c("onLoad", "attach", "detach", "onUnload")}   & 470566 &      6.9\%\\
    \c{c("append", "prepend", "replace")} &              261587&       3.9\% \\
    \c{c("left", "right", "centre", "none")} & 162086     & 2.4\%\\
    \c{c("no", "ifany", "always")}   &                71580 &       1.1\%\\
    \c{c("pearson", "kendall", "spearman")}  & 72962 &      1.1\%\\
    \c{\<NULL\>}& 75330  &      1.1\% \\
    \c{\<Integer Vector\>}&                 66279&       1\%\\\hline
  \end{tabular}
  \caption{Top ten eval calls in Core}
  \label{A}
\end{table*}

The most frequent ten expressions to eval calls from CRAN packages contribute to
90\% of all \eval calls.
\begin{table*}[tb]
  \centering
  \begin{tabular}{l|rr} \hline
    Expression & Eval Call & Eval Call \% \\\hline
    \c{\<Environment\>} &                                                                                                                           1091474   &  68.2\%\\
    \c{column[rows] <<- what} &                                                                                                         55677    &   3.5\%\\
    \c{function(value) freduce(value, `_function_list`)} &                                                                              37251   &    2.3\%\\
    \c{c("default", "default2012", "default2011" ...}&      20610      & 1.3\%\\
    \c{force(..1)}                                        &                                                                             20461     &  1.3\%\\
    \c{alist(`_spec`)}                                   &                                                                              18532    &   1.2\%\\
    \c{inner}                                           &                                                                               18530   &    1.2\%\\
    \c{slot(family, "fini")}                           &                                                                                 7288   &    0.5\%\\
    \c{\~fitted(.)}                                    &                                                                                  4733   &    0.3\%\\
    \c{function(.) purrr::keep(., is.function)}      &                                                                                   4344  &     0.3\%\\\hline
  \end{tabular}
  \caption{Top ten eval calls in CRAN}
  \label{A}
\end{table*}
